Multi-modality Imagery Database for Plant Phenotyping

### 2015-04-13 datapaper.tex
Jeff's content

\title{Data Paper%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\begin{abstract}
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}\label{intro}
Text with citations \cite{RefB} and \cite{RefJ}.

\section{Background} \label{sec:1}

@@

@@

@@

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{RefJ}
% Format for Journal Reference
Author, Article title, Journal, Volume, page numbers (year)
% Format for books
\bibitem{RefB}
Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

\end{document}
% end of file template.tex

>>>>

\title{Multi-modality Imagery Database for Plant Phenotyping %\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\begin{abstract}
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{Plant Phenotyping  \and Computer Vision \and Plant image \and Leaf segmentation \and Leaf tracking\and Multiple sensors \and Arabidopsis \and Bean}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\input{datapaper_intro.tex}

\input{datapaper_prior.tex}

@@

\subsection{Plants}

\input{datapaper_plants.tex}

@@

\input{datapaper_hardware.tex}

@@

{\small
\bibliographystyle{springer}
%\bibliography{/Sharefolder/Dropbox/Bibliographies/abbrev_brief,/Sharefolder/Dropbox/Bibliographies/xl-literature}
\bibliography{abbrev_brief,xl-literature}
}
\end{document}
% end of file template.tex
